Experience Report: Haskell in Computational Biology

### 2012-07-01 mrfy_experience_report.tex
plainnat bibstyle
correct graph
parallel dangling ref pulled

Because \mrfy\ works on many subproblems independently, we~found it easy
to improve performance through parallelism.
Calls on query sequences between beta strands are independent,
as are calls on different placements.
Using
\texttt{Control.Parallel}, parallelizing this computation was as easy
as  substituting
\texttt{parmap rseq} for \texttt{map}.
On a 48-core, 2.3GHz AMD Opteron 6176 system, 
parallel performance is good up to about 12~cores.
\figref{fig:efficiency} shows parallel efficiency when
using a model of an ``8-bladed beta propeller;''
the model has 165 ordinary nodes and 40~beta strands totalling
178 nodes.
We~benchmarked \mrfy\ using a query sequence of
592 amino acids.
Figure~\ref{fig:speedup} SHOWS NOTHING OF VALUE BECAUSE RANDOMNESS
BREAKS EVERYTHING.  AND IT SHOULD HAVE ERROR BARS.
(Parallel efficiency is 1.0 when the speedup is equal to the number of cores
used.
Lower speedups mean lower efficiency.)

@@

\begin{figure}%%%[h!]
\centerline{\includegraphics{efficiency}}
\bigskip
\caption{\mrfy's WRONG parallel efficiency}
\label{fig:efficiency}
\end{figure}

@@

\bibliographystyle{abbrvnat}

@@

\break

\begin{figure}%%%[h!]
\centerline{\includegraphics{speedup}}
\bigskip
\caption{\mrfy's parallel speedup}
\label{fig:speedup}
\end{figure}

>>>>

Because \mrfy\ works on many subproblems independently, we~found it easy
to improve performance through parallelism.
Calls on query sequences between beta strands are independent,
as are calls on different placements.
Using
\texttt{Control.Parallel}, parallelizing this computation was as easy
as  substituting
\texttt{parmap rseq} for \texttt{map}.
On a 48-core, 2.3GHz AMD Opteron 6176 system, 
parallel performance is good up to about 12~cores.
\figref{fig:speedup} shows speedup when
using a model of an ``8-bladed beta propeller'' with 1~to~48 cores.
The model has 165 ordinary nodes and 40~beta strands totalling
178 nodes; the benchmark query sequence has
592 amino acids.
AND WHAT DO WE CONCLUDE FROM THE FIGURE, JOHNNY?

@@

\begin{figure}%%%[h!]
\centerline{\includegraphics{speedup}}
\bigskip
\caption{Parallel speedup}
\label{fig:speedup}
\end{figure}

@@

\bibliographystyle{plainnat}

@@

% \break
% 
% 
% \begin{figure}%%%[h!]
% \centerline{\includegraphics{efficiency}}
% \bigskip
% Beautiful $\frac 1 {\log p}$!
% \caption{\mrfy's parallel efficiency}
% \label{fig:speedup}
% \end{figure}
